---
title: "Downloads"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

All data is hosted on this site and mirrored in the
[GitHub repository](https://github.com/slub/tu9-jct-data) — outputs under
[`data/`](https://github.com/slub/tu9-jct-data/tree/main/data), pipeline inputs
under [`data-raw/`](https://github.com/slub/tu9-jct-data/tree/main/data-raw).

## Files

Two views — agreements and the journals they cover:

- [`agreements.csv`](agreements.csv) — every agreement with at least one TU9 participant
- [`journals.csv`](journals.csv) — every journal covered by those agreements

Per institution (the same two views):

```{r}
#| echo: false
#| output: asis
for (x in meta$institutions) {
  cat(sprintf(
    "- `institutions/%s/` — [agreements.csv](institutions/%s/agreements.csv) · [journals.csv](institutions/%s/journals.csv)\n",
    x$slug, x$slug, x$slug))
}
```

ESAC enrichment:

- [`esac.csv`](esac.csv) — ESAC-registered agreements with id, name, publisher, consortium and dates

Pipeline inputs:

- [`orgs.csv`](orgs.csv) — TU9 institutions and their ROR IDs
- [`urls.csv`](urls.csv) — each institution's open-access agreements and funding page

Other:

- [`meta.json`](meta.json) — summary counts and last-updated date
- [`DATA-LICENSE`](DATA-LICENSE) — the data licence (CC0 1.0)
