---
title: "TU9 Transformative Agreements"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

This site lists transformative-agreement metadata for the
[TU9](https://www.tu9.de/) universities — the alliance of leading German
institutes of technology. The data comes from the
[Journal Checker Tool](https://journalcheckertool.org/transformative-agreements/)
("Transformative Agreements Public Data", released under
[CC0](https://creativecommons.org/publicdomain/zero/1.0/)) and is refreshed
automatically every week. Agreement names, publishers and consortia are enriched
from the [ESAC Transformative Agreement Registry](https://esac-initiative.org/about/transformative-agreements/agreement-registry/).

An agreement is listed for a university when any of that university's
[ROR](https://ror.org/) identifiers appears among the agreement's
participating institutions. Matching is intentionally strict (precision
first): a university is represented only by ROR ids it explicitly claims. This
includes a university's own library where that library has its own ROR — for
example Dresden also counts agreements held by the [SLUB](https://ror.org/03wf51b65)
and Hannover those held by the [TIB](https://ror.org/04aj4c181). University
clinics are deliberately not counted: in this data they only ever appear on
agreements where the university itself is already listed, so they add no
coverage.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covering **%d** agreement records and **%d** unique journals.*\n",
  meta$updated, meta$n_agreements, meta$n_journals))
```

## Coverage by institution

```{r}
#| echo: false
inst <- meta$institutions
df <- data.frame(
  Institution  = vapply(inst, function(x) x$name, character(1)),
  Agreements   = vapply(inst, function(x) x$n_agreements, integer(1)),
  Journals     = vapply(inst, function(x) x$n_journals, integer(1)),
  slug         = vapply(inst, function(x) x$slug, character(1)),
  ror          = vapply(inst, function(x) x$ror_id, character(1)),
  stringsAsFactors = FALSE
)
reactable(
  df,
  sortable = TRUE, defaultPageSize = 9, highlight = TRUE,
  columns = list(
    Institution = colDef(cell = function(value, index) {
      htmltools::tags$a(href = sprintf("institutions/%s.html", df$slug[index]), value)
    }),
    Agreements = colDef(name = "Agreements"),
    Journals   = colDef(name = "Journals"),
    slug = colDef(show = FALSE),
    ror  = colDef(name = "ROR", html = TRUE, cell = function(value) {
      ids <- strsplit(value, ";", fixed = TRUE)[[1]]
      links <- vapply(ids, function(id) as.character(
        htmltools::tags$a(href = paste0("https://ror.org/", id),
                          target = "_blank", id)), character(1))
      paste(links, collapse = ", ")
    })
  )
)
```

## Data downloads

All data is published as plain CSV in the
[`data/` directory](https://github.com/slub/tu9-jct-data/tree/main/data) of the
repository.

Two views — agreements and the journals they cover — for all TU9 universities
together and per institution:

- `data/agreements.csv` — every agreement with at least one TU9 participant
- `data/journals.csv` — every journal covered by those agreements
- `data/<institution>/` — the same two views for a single institution

Plus the ESAC registry metadata they are enriched with:

- `data/esac.csv` — ESAC-registered agreements with id, name, publisher, consortium and dates
