---
title: "TU9 Transformative Agreements"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Researchers at TU9 universities can publish open access in many journals
through transformative agreements their institutions have negotiated with
publishers. This site lists those [agreements](agreements.qmd) and the
[journals](journals.qmd) each one covers, both alliance-wide and per
institution.

The data comes from the Journal Checker Tool (JCT), enriched with agreement
names, publishers and consortia from the ESAC registry. It's refreshed weekly
and released under CC0.

See [Background](background.qmd) for how the JCT assembles this data and how
agreements are matched to TU9 universities.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covers **%s** agreement records and **%s** unique journals.*\n",
  meta$updated, fmt_int(meta$n_agreements), fmt_int(meta$n_journals)))
```

## Coverage by institution

```{r}
#| echo: false
inst <- meta$institutions
df <- data.frame(
  Institution  = vapply(inst, function(x) x$name, character(1)),
  Agreements   = vapply(inst, function(x) x$n_agreements, integer(1)),
  Journals     = vapply(inst, function(x) x$n_journals, integer(1)),
  slug         = vapply(inst, function(x) x$slug, character(1)),
  ror          = vapply(inst, function(x) x$ror_id, character(1)),
  stringsAsFactors = FALSE
)
reactable(
  df,
  sortable = TRUE, defaultPageSize = 9, highlight = TRUE,
  columns = list(
    Institution = colDef(cell = function(value, index) {
      htmltools::tags$a(href = sprintf("institutions/%s.html", df$slug[index]), value)
    }),
    Agreements = colDef(name = "Agreements"),
    Journals   = colDef(name = "Journals", format = colFormat(separators = TRUE, locales = "en-US")),
    slug = colDef(show = FALSE),
    ror  = colDef(name = "ROR ID", html = TRUE, cell = function(value) {
      ids <- strsplit(value, ";", fixed = TRUE)[[1]]
      links <- vapply(ids, function(id) as.character(
        htmltools::tags$a(href = paste0("https://ror.org/", id),
                          target = "_blank", id)), character(1))
      paste(links, collapse = ", ")
    })
  )
)
```

## Downloads

All views are available as plain CSV — hosted on this site and in the
repository. See the [Downloads](downloads.qmd) page.
