---
title: "TU9 Transformative Agreements"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

This site lists **transformative-agreement** metadata for the
[TU9](https://www.tu9.de/) universities — the alliance of leading German
institutes of technology. The data comes from the
[Journal Checker Tool](https://journalcheckertool.org/transformative-agreements/)
("Transformative Agreements Public Data", released under
[CC0](https://creativecommons.org/publicdomain/zero/1.0/)) and is refreshed
automatically every week.

An agreement is listed for a university when that university's exact
[ROR](https://ror.org/) identifier appears among the agreement's participating
institutions. Matching is intentionally **strict** (precision first): closely
related entities such as separate libraries or university clinics are *not*
counted yet.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covering **%d** agreement records and **%d** unique journals.*\n",
  meta$updated, meta$n_agreements, meta$n_journals))
```

## Coverage by institution

```{r}
#| echo: false
inst <- meta$institutions
df <- data.frame(
  Institution  = vapply(inst, function(x) x$name, character(1)),
  Agreements   = vapply(inst, function(x) x$n_agreements, integer(1)),
  Journals     = vapply(inst, function(x) x$n_journals, integer(1)),
  slug         = vapply(inst, function(x) x$slug, character(1)),
  ror          = vapply(inst, function(x) x$ror_id, character(1)),
  stringsAsFactors = FALSE
)
reactable(
  df,
  sortable = TRUE, defaultPageSize = 9, highlight = TRUE,
  columns = list(
    Institution = colDef(cell = function(value, index) {
      htmltools::tags$a(href = sprintf("institutions/%s.html", df$slug[index]), value)
    }),
    Agreements = colDef(name = "Agreements"),
    Journals   = colDef(name = "Journals"),
    slug = colDef(show = FALSE),
    ror  = colDef(name = "ROR", cell = function(value) {
      htmltools::tags$a(href = paste0("https://ror.org/", value),
                        target = "_blank", value)
    })
  )
)
```

## Data downloads

All views are available as plain CSV files in the
[`data/` directory](https://github.com/slub/tu9-jct-data/tree/main/data) of the
repository:

- `data/agreements.csv` — every agreement with at least one TU9 participant
- `data/journals.csv` — every journal covered by those agreements
- `data/<institution>/` — the same two views for a single institution
