---
title: "TU9 Transformative Agreements"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

This site is a TU9 view of the
[Journal Checker Tool](https://journalcheckertool.org/transformative-agreements/)
(JCT) index of
[Plan S–compliant](https://www.coalition-s.org/faq-theme/compliance/)
transformative agreements. It covers the
[TU9](https://www.tu9.de/) universities — the alliance of leading German
institutes of technology. The data is released under
[CC0](https://creativecommons.org/publicdomain/zero/1.0/), refreshed weekly, and
enriched with agreement names, publishers and consortia from the
[ESAC registry](https://esac-initiative.org/about/transformative-agreements/agreement-registry/).

An agreement is listed for a university when one of that university's
[ROR](https://ror.org/) identifiers is among the agreement's participating
institutions. See [Background](background.qmd) for how the JCT assembles this
data and how matching works.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covering **%d** agreement records and **%d** unique journals.*\n",
  meta$updated, meta$n_agreements, meta$n_journals))
```

## Coverage by institution

```{r}
#| echo: false
inst <- meta$institutions
df <- data.frame(
  Institution  = vapply(inst, function(x) x$name, character(1)),
  Agreements   = vapply(inst, function(x) x$n_agreements, integer(1)),
  Journals     = vapply(inst, function(x) x$n_journals, integer(1)),
  slug         = vapply(inst, function(x) x$slug, character(1)),
  ror          = vapply(inst, function(x) x$ror_id, character(1)),
  stringsAsFactors = FALSE
)
reactable(
  df,
  sortable = TRUE, defaultPageSize = 9, highlight = TRUE,
  columns = list(
    Institution = colDef(cell = function(value, index) {
      htmltools::tags$a(href = sprintf("institutions/%s.html", df$slug[index]), value)
    }),
    Agreements = colDef(name = "Agreements"),
    Journals   = colDef(name = "Journals"),
    slug = colDef(show = FALSE),
    ror  = colDef(name = "ROR", html = TRUE, cell = function(value) {
      ids <- strsplit(value, ";", fixed = TRUE)[[1]]
      links <- vapply(ids, function(id) as.character(
        htmltools::tags$a(href = paste0("https://ror.org/", id),
                          target = "_blank", id)), character(1))
      paste(links, collapse = ", ")
    })
  )
)
```

## Downloads

All views are available as plain CSV — hosted on this site and in the
repository. See the [Downloads](downloads.qmd) page.
