---
title: "TU9 Transformative Agreements"
---

```{r}
#| echo: false
source("scripts/site_helpers.R")
meta <- read_meta()
```

Researchers at the TU9 universities can publish open access in many journals
through transformative agreements their institutions have negotiated with
publishers. This site lists those agreements and the journals each one covers —
across all nine universities of technology in the TU9 alliance, and per
institution.

The data comes from the Journal Checker Tool (JCT) — refreshed weekly, released
under CC0, and enriched with agreement names, publishers and consortia from the
ESAC registry.

See [Background](background.qmd) for how the JCT assembles this data and how
agreements are matched to TU9 universities.

```{r}
#| echo: false
#| output: asis
cat(sprintf(
  "*Last updated: **%s**. Covering **%d** agreement records and **%d** unique journals.*\n",
  meta$updated, meta$n_agreements, meta$n_journals))
```

## Coverage by institution

```{r}
#| echo: false
inst <- meta$institutions
df <- data.frame(
  Institution  = vapply(inst, function(x) x$name, character(1)),
  Agreements   = vapply(inst, function(x) x$n_agreements, integer(1)),
  Journals     = vapply(inst, function(x) x$n_journals, integer(1)),
  slug         = vapply(inst, function(x) x$slug, character(1)),
  ror          = vapply(inst, function(x) x$ror_id, character(1)),
  stringsAsFactors = FALSE
)
reactable(
  df,
  sortable = TRUE, defaultPageSize = 9, highlight = TRUE,
  columns = list(
    Institution = colDef(cell = function(value, index) {
      htmltools::tags$a(href = sprintf("institutions/%s.html", df$slug[index]), value)
    }),
    Agreements = colDef(name = "Agreements"),
    Journals   = colDef(name = "Journals"),
    slug = colDef(show = FALSE),
    ror  = colDef(name = "ROR", html = TRUE, cell = function(value) {
      ids <- strsplit(value, ";", fixed = TRUE)[[1]]
      links <- vapply(ids, function(id) as.character(
        htmltools::tags$a(href = paste0("https://ror.org/", id),
                          target = "_blank", id)), character(1))
      paste(links, collapse = ", ")
    })
  )
)
```

## Downloads

All views are available as plain CSV — hosted on this site and in the
repository. See the [Downloads](downloads.qmd) page.
